The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-13 Paper_third_version/Article_UV_Mexico.tex
Proposed changes by Piacentini

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 35\% in
  2000 and 20\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite- and ground-based UVI, and showed specific
  contributions from aerosols in the boundary layer and the free troposphere,
  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
  decreasing order of importance. Such large changes in UV radiation
  between 2000 and 2019 have important implications ranging from human
  health (skin cancer and cataract induction) to air pollution control
  (photochemical smog formation).
\end{abstract}

@@

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-predicted feedbacks between chemistry and radiation.~~

The environment of Mexico City is of particular interest for several
reasons: (1) Nearly 23 million people inhabit the Mexico City
Metropolitan Area (MCMA), and the UV environment has direct implications
for their health, both in terms of skin/eye UV exposure and~\emph{via}
photochemical smog formation. (2) As a tropical megacity, it is to some
extent representative of the situation of many others, with year-round
intense midday UV irradiance, a shallower atmosphere due to the city's
high elevation of 2240 m above sea level, and a transition toward newer
and cleaner technologies, leading to gradual improvements in air
quality. (3) Air quality within MCMA has undergone extensive scrutiny,
with a well-established monitoring network operating since
1986,\cite{RAMA}
numerous intensive field campaigns to study the
meteorology, emissions, and photochemistry of smog
formation,\citep{Doran_1998,Molina_2007,Molina_2010}
and numerical modeling incorporating the
evolving knowledge.\citep{Jazcilevich_2005,Tie_2007,Zhang_2009,Zavala_2020}
This extensive body of knowledge
provides the foundation for understanding our study.

Here, we analyze two decades of continuous measurements of the UV Index
at multiple locations within the MCMA, collected by the Secretariat of
the Environment (Secretaría del Medio Ambiente,
SEDEMA)\footnote{\url{https://www.sedema.cdmx.gob.mx/}} of the Mexico
City government as part of an intensive monitoring network over the
MCMA. The UV Index is defined as:

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for typical cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
The selection of cloud-free days was aided by comparison of the measurements
with the TUV model predictions for clear skies, with prolonged deviations and
fluctuations usually indicative of cloudy conditions.However,
during the rainy period (from June to October) at least a brief episode of clouds,
is seen at CHO station around noon in 13 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
is a result of the station’s location farther away from pollution sources,
both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.49\columnwidth]{figures/Histogram}
    \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
    during 2000-2019.
    {\label{461017}}%
    }}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.71\columnwidth]{figures/Monthly_mean_RD.png}
  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

@@

The observed changes in the concentrations of these air pollutants have
significant implications for surface UV radiation, as can be
demonstrated with the TUV radiative transfer model.
Table~{\ref{table:TUVmodel}} summarizes UVI values for
the June-July time period, estimated by the three methods: OMI
satellite-derived UVI, SIMAT ground-based observations, and TUV modeling
using air pollution estimates. Two groups of values can be readily
identified: (1) SIMAT daily record values, OMI with or without BL
aerosols, and TUV for very clean conditions, all with UVI values around
15-16; and (2) the average of daily maxima of SIMAT observations and TUV UVI results using
MCMA pollutants as input. Note that SIMAT and TUV value are in good agreement
for both 2000-2001 and 2018-2019 and are considerably lower than for group (1). Compared to the OMI
estimate that included the climatological absorbing aerosol correction (15.3),
observed SIMAT values were lower by 35\% in 2000 and by 20\% in 2019.
Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
relative to the TUV values of 15.6 for a pristine atmosphere.

@@

The reductions in surface UV radiation with respect to an ideally clear
atmosphere -- by nearly 40\% in 2000 and still 20\% in 2020 -- are
large, both within the context of human UV exposure and air quality
mitigation. In urban areas where ozone production scales proportionally
with UV levels and with volatile organic compound~(VOC) emissions (the
VOC-limited regime), a 10\% increase in BL average photolysis rates
means that VOC emissions will need to be reduced by 10\% to meet the
same goals, or else successful reductions in aerosols would lead to
unwanted UV-driven increases in O\textsubscript{3}.~Such UV changes must
be considered carefully in air quality mitigation strategies. For human
exposure, a 20\% increase in UV irradiances over two decades should be
seen as a non-negligible public health issue requiring some reassessment
of preventive behaviors to minimize the risk of skin cancer, cataract,
and other UV-related health effects. The efforts that Mexico City has
made to improve air quality have reduced levels
of most air pollutants. Nevertheless, they caused an increase in UV
radiation that reaches the surface.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
  We wish to acknowledge the staff of SIMAT, from the Secretariat of
  Environment, for the data and the continuous assistance during the
  realization of this project. Adriana Ipiña would like to extend her
  thanks to Dirección General de Personal Académico, Universidad
  Nacional Autónoma de México (DGAPA-UNAM) for the postdoctoral fellowship
  at Centro de Ciencias de la Atmósfera of the UNAM. Rubén D Piacentini
  wishes to thank CONICET and National University of Rosario, Argentina,
  for their partial support to the present work. The National Center for
  Atmospheric Research is sponsored by the National Science Foundation.
\end{acknowledgement}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 40\% in
  2000 and 25\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite- and ground-based UVI, and showed specific
  contributions from aerosols in the boundary layer and the free troposphere,
  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
  decreasing order of importance. Such large changes in UV radiation
  between 2000 and 2019 have important implications ranging from human
  health (skin cancer and cataract induction) to air pollution control
  (photochemical smog formation).
\end{abstract}

@@

The question of how air pollution alters the urban UV radiation environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-predicted feedbacks between chemistry and radiation.~~

The environment of Mexico City is of particular interest for several
reasons: (1) Nearly 23 million people inhabit the Mexico City
Metropolitan Area (MCMA), and the UV radiation environment has direct implications
for their health, both in terms of skin/eye UV exposure and~\emph{via}
photochemical smog formation. (2) As a tropical megacity, it is to some
extent representative of the situation of many others, with year-round
intense midday UV irradiance, a shallower atmosphere due to the city's
high elevation of 2240 m above sea level, and a transition toward newer
and cleaner technologies, leading to gradual improvements in air
quality. (3) Air quality within MCMA has undergone extensive scrutiny,
with a well-established monitoring network operating since
1986,\cite{RAMA}
numerous intensive field campaigns to study the
meteorology, emissions, and photochemistry of smog
formation,\citep{Doran_1998,Molina_2007,Molina_2010}
and numerical modeling incorporating the
evolving knowledge.\citep{Jazcilevich_2005,Tie_2007,Zhang_2009,Zavala_2020}
This extensive body of knowledge
provides the foundation for understanding our study.

In this work, we analyze two decades of continuous measurements of the UV Index
at multiple locations within the MCMA, collected by the Secretariat of
the Environment (Secretaría del Medio Ambiente,
SEDEMA)\footnote{\url{https://www.sedema.cdmx.gob.mx/}} of the Mexico
City government as part of an intensive monitoring network over the
MCMA. The UV Index is defined as:

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for typical cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
The selection of cloud-free days was aided by comparison of the measurements
with the TUV model predictions for clear skies, with prolonged deviations and
fluctuations usually indicative of cloudy conditions. However,
during the rainy period (from June to October) at least a brief episode of clouds,
is seen at CHO station around noon on 23 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
is a result of the station’s location farther away from pollution sources,
both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.49\columnwidth]{figures/Histogram}
    \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
    for the period 2000-2019.
    {\label{461017}}%
    }}
  \end{center}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

@@

The observed changes in the concentrations of these air pollutants have
significant implications for surface UV radiation, as can be
demonstrated with the TUV radiative transfer model.
Table~{\ref{table:TUVmodel}} summarizes UVI values for
the June-July time period, estimated by the three methods: OMI
satellite-derived UVI, SIMAT ground-based observations, and TUV modeling
using air pollution estimates. Two groups of values can be readily
identified: (1) SIMAT daily record values, OMI with or without BL
aerosols, and TUV for very clean conditions, all with UVI values around
15-16; and (2) the average of daily maxima of SIMAT observations and TUV UVI results using
MCMA pollutants as input. Note that SIMAT and TUV value are in good agreement
for both 2000-2001 and 2018-2019 and are considerably lower than for group (1). Compared to the OMI
estimate that included the climatological absorbing aerosol correction (16.6),
observed SIMAT values were lower by 40\% in 2000 and by 25\% in 2019.
Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
relative to the TUV values of 15.6 for a pristine atmosphere.

@@

The reductions in surface UV radiation with respect to an ideally clear
atmosphere -- by nearly 40\% in 2000 and still 20\% in 2019 -- are
large, both within the context of human UV exposure and air quality
mitigation. In urban areas where ozone production scales proportionally
with UV levels and with volatile organic compound~(VOC) emissions (the
VOC-limited regime), a 10\% increase in BL average photolysis rates
means that VOC emissions will need to be reduced by 10\% to meet the
same goals, or else successful reductions in aerosols would lead to
unwanted UV-driven increases in O\textsubscript{3}.~Such UV changes must
be considered carefully in air quality mitigation strategies. For human
exposure, a 20\% increase in UV irradiances over two decades should be
seen as a non-negligible public health issue requiring some reassessment
of preventive behaviors to minimize the risk of skin cancer, cataract,
and other UV-related health effects. The efforts that Mexico City has
made to improve air quality have reduced levels
of most air pollutants. Nevertheless, they caused an increase in UV
radiation that reaches the surface.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
  We wish to acknowledge the staff of SIMAT, from the Secretariat of
  Environment, for the data and the continuous assistance during the
  realization of this project. Adriana Ipiña would like to extend her
  thanks to Dirección General de Personal Académico, Universidad
  Nacional Autónoma de México (DGAPA-UNAM) for the postdoctoral fellowship
  at Centro de Ciencias de la Atmósfera of the UNAM. Rubén D Piacentini
  wishes to thank CONICET and National University of Rosario, Argentina,
  for their partial support to the present work. We thank Dr. Jay Herman
  (University of Maryland Baltimore County) for useful discussions. The National Center for
  Atmospheric Research is sponsored by the National Science Foundation.
\end{acknowledgement}
